---
title: "HW2"
author: "LeeAnn Stover"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Reporting a binomial test

```{r}
prep <- 501
doubobj <- 1859
binom.test(doubobj, (prep + doubobj), .5)
```

##### Out of 2360 dative constructions uttered during spontaneous phone conversations, 1,859 double objects were found. If the null hypothesis posits a 50% probability of double object constructions, the null hypothesis can be rejected given this data. probability of success: 78.8%, CI: 0.77 - 0.80, p < .001

### McNemar's test
```{r}
df <- read.csv("~/Desktop/GraduateCenter/Stats/PTB.tsv", sep = "\t", header = TRUE)
Stan.correct <- df$Stanford.tag == df$gold.tag
NLP4J.correct <- df$NLP4J.tag == df$gold.tag
x1 <- sum(Stan.correct & !NLP4J.correct)
x2 <- sum(NLP4J.correct & !Stan.correct)
print(x1)
print(x2)
binom.test(min(x1, x2), (x1 + x2), 0.5)
```
##### Stanford wins = 943, NLP4J wins = 1016. The null hypothesis cannot be rejected: Neither tagger performs better than the other. 